---
title: "Project"
author: "TaoZhang, Gefei Shen, Xuhao Wang, simon xiong"
date: "2024-11-10"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(reshape2)
library(corrplot)
library(ggcorrplot)
library(shiny)
```


```{r, echo=FALSE}
data <- read.csv("./data/user_behavior_dataset.csv")

```


### Question 1: What is the preferred operating system for each age group?


```{r, echo=FALSE}
data$Age_Group <- cut(data$Age, breaks = c(18, 28, 38, 48, 60, Inf), 
                      labels = c("18-28", "29-38", "39-48", "49-60", "60+"), right = FALSE)

selectInput("age_group", "Select Age Group:", 
            choices = unique(data$Age_Group), 
            selected = unique(data$Age_Group)[1])

renderPlot({
  filtered_data <- data %>%
    filter(Age_Group == input$age_group) %>%
    group_by(Operating.System) %>%
    summarise(Count = n()) %>%
    mutate(Percentage = Count / sum(Count) * 100)
  
  ggplot(filtered_data, aes(x = "", y = Percentage, fill = Operating.System)) +
    geom_bar(stat = "identity", width = 1) +
    coord_polar("y") +
    labs(title = paste("Operating System Distribution - Age Group:", input$age_group),
         fill = "Operating System") +
    theme_void() +
    geom_text(aes(label = paste0(round(Percentage, 1), "%")), 
              position = position_stack(vjust = 0.5))
})
```


This chart shows the preference for operating systems (Android and iOS) by age group, revealing the proportion of users in each age group who use the different systems. As can be seen from the chart, Android dominates across all age groups, with the percentage of users ranging between 78% and 80%, demonstrating dominance. In contrast, iOS has a lower percentage of users, holding steady at around 20 per cent.

In terms of age groups, although iOS has seen a small rise in the older 49-60 age group (to 22 per cent), overall this change has not altered the dominance of Android across all age groups. There is a general preference for Android across all age groups, with Android particularly favoured in the younger to middle age group (18-48).



### Question 2: How does screen time vary by different age groups?

```{r, echo=FALSE}
screen_time <- data %>%
  group_by(Age_Group, Gender) %>%
  summarise(Average_Screen_Time = mean(Screen.On.Time..hours.day., na.rm = TRUE), .groups = "drop")

selectInput("gender_q2", "Select Gender or Combined Data:",
            choices = c("Both (Combined)", unique(data$Gender)))

renderPlot({
  if (input$gender_q2 == "Both (Combined)") {
    screen_time_combined <- data %>%
      group_by(Age) %>%
      summarise(Average_Screen_On_Time = mean(Screen.On.Time..hours.day., na.rm = TRUE), .groups = "drop")
    
    ggplot() +
      geom_point(data = data, aes(x = Age, y = Screen.On.Time..hours.day., color = "Combined"), alpha = 0.4) +
      geom_smooth(data = screen_time_combined, aes(x = Age, y = Average_Screen_On_Time, color = "Combined"),
                  method = "loess", span = 0.3, se = FALSE) +
      scale_color_manual(values = c("Combined" = "black"), labels = c("Combined" = "Combined (Both Genders)")) +
      labs(
        title = "Average Screen On Time by Age (Combined for Both Genders)",
        x = "Age",
        y = "Average Screen On Time (hours/day)",
        color = "Legend"
      ) +
      theme_minimal()
    
  } else {
    screen_time_individual <- data %>%
      filter(Gender == input$gender_q2) %>%
      group_by(Age) %>%
      summarise(Average_Screen_On_Time = mean(Screen.On.Time..hours.day., na.rm = TRUE), .groups = "drop")
    
    gender_color <- ifelse(input$gender_q2 == "Male", "blue", "red")
    
    ggplot(screen_time_individual, aes(x = Age, y = Average_Screen_On_Time, color = input$gender_q2)) +
      geom_point(alpha = 0.6) +
      geom_smooth(method = "loess", span = 0.3, se = FALSE) +
      scale_color_manual(values = setNames(c(gender_color), input$gender_q2),
                         labels = setNames(input$gender_q2, input$gender_q2)) +
      labs(
        title = paste("Average Screen On Time by Age (Gender:", input$gender_q2, ")"),
        x = "Age",
        y = "Average Screen On Time (hours/day)",
        color = "Legend"
      ) +
      theme_minimal()
  }
})
```


In this plot, the x-axis represents the age of the user, and the y-axis shows the average screen usage time (in hours per day). The red and blue dots represent individual observations of screen usage time for females and males at different ages, respectively. Each dot indicates the average screen time for a specific gender at a particular age.In this plot, we use a smooth curve to display the overall trend to give audience a better and more intuitive comparion. We can observe a peak in screen usage time for males around 50 years old, while for females, there is a peak around 35 years old. Otherwise, the average screen usage time is similar for both genders.





### Question 3: Does the amount of time spent on the phone daily correlate with the number of apps in that person's phone?


```{r, echo=FALSE}
correlation_data <- data %>%
  select(App.Usage.Time..min.day., Screen.On.Time..hours.day., Number.of.Apps.Installed, Age)

selectInput(
  inputId = "vars_q3",
  label = "Select Variables for Correlation Analysis:",
  choices = c(
    "Screen On Time (hours/day)" = "Screen.On.Time..hours.day.",
    "App Usage Time (min/day)" = "App.Usage.Time..min.day.",
    "Number of Apps Installed" = "Number.of.Apps.Installed",
    "Battery Drain (mAh/day)" = "Battery.Drain..mAh.day.",
    "Data Usage (MB/day)" = "Data.Usage..MB.day.",
    "Age" = "Age"
  ),
  selected = c("Screen.On.Time..hours.day.", "App.Usage.Time..min.day.", "Number.of.Apps.Installed"),
  multiple = TRUE
)

renderPlot({
  req(length(input$vars_q3) >= 2)
  
  correlation_data <- data %>%
    select(all_of(input$vars_q3))
  
  correlation_matrix <- cor(correlation_data, use = "complete.obs")
  
  corrplot(
    correlation_matrix,
    method = "color",       
    type = "upper",         
    tl.srt = 45,            
    title = "Dynamic Correlation Matrix",
    addCoef.col = "red"   
  )
})

```


Based on question 2, we want to further explore the relationship between screen using time and number of apps. This correlation matrix reveals strong interconnections between app usage time, screen-on time, and the number of apps installed. Specifically, app usage time has a very high positive correlation with both screen-on time and the number of apps installed, indicating that users who install more apps tend to spend more time using them and consequently keep their screens on longer. However, age shows almost no correlation with these variables, I think this is due to the fact that the data set was not sampled randomly, but the average of all ages was asked.


### Question 4
```{r, echo=FALSE}
data$Age_Group <- cut(data$Age, breaks = c(18, 28, 38, 48, 60, Inf), 
                      labels = c("18-28", "29-38", "39-48", "49-60", "60+"), right = FALSE)

selectInput(
  inputId = "age_groups_q4",
  label = "Add Age Groups:",
  choices = unique(data$Age_Group),
  selected = unique(data$Age_Group)[1],  # Default selection
  multiple = TRUE  # Allow selecting multiple age groups
)

renderPlot({
  filtered_data <- data %>%
    filter(Age_Group %in% input$age_groups_q4)
  
  ggplot(filtered_data, aes(x = Age_Group, y = App.Usage.Time..min.day., fill = Age_Group)) +
    geom_boxplot(outlier.color = "red", outlier.shape = 1) +
    scale_fill_brewer(palette = "Set3") +                 
    labs(
      title = "Distribution of App Usage Time Across Selected Age Groups",
      x = "Age Group",
      y = "Daily App Usage Time (minutes)"
    ) +
    theme_minimal()
})

```




### Question 5: Is the use of operating systems correlated with the length of screen usage?

```{r, echo=FALSE}
selectInput(
  inputId = "os_q5",
  label = "Select Operating System:",
  choices = c("All", unique(data$Operating.System)),
  selected = "All"
)

renderPlot({
  filtered_data <- if (input$os_q5 != "All") {
    data %>% filter(Operating.System == input$os_q5)
  } else {
    data
  }
  
  ggplot(filtered_data, aes(x = Operating.System, y = Screen.On.Time..hours.day., fill = Operating.System)) +
    geom_boxplot(outlier.color = "red", outlier.shape = 1) +
    scale_fill_brewer(palette = "Set3") +
    labs(
      title = paste("Screen On Time by Operating System (Filtered:", input$os_q5, ")"),
      x = "Operating System",
      y = "Screen On Time (hours/day)"
    ) +
    theme_minimal() +
    theme(legend.position = "none")
})
```

### Question 6: Is this is a fake dataset?
```{r, echo=FALSE}
selectInput(
  inputId = "os_q6",
  label = "Select Operating System:",
  choices = c("All", unique(data$Operating.System)),
  selected = "All"
)

renderPlot({
  filtered_data <- if (input$os_q6 != "All") {
    data %>% filter(Operating.System == input$os_q6)
  } else {
    data
  }
  
  ggplot(filtered_data, aes(x = App.Usage.Time..min.day.)) +
    geom_histogram(binwidth = 30, fill = "lightblue", color = "darkblue") +
    labs(
      title = paste("App Usage Time Frequency (Filtered:", input$os_q6, ")"),
      x = "App Usage Time (minutes/day)",
      y = "Frequency"
    ) +
    theme_minimal()
})

renderPlot({
  filtered_data <- if (input$os_q6 != "All") {
    data %>% filter(Operating.System == input$os_q6)
  } else {
    data
  }
  
  ggplot(filtered_data, aes(x = App.Usage.Time..min.day., y = Number.of.Apps.Installed)) +
    geom_point(alpha = 0.6, color = "blue") +
    labs(
      title = paste("App Usage Time vs Daily App Usage (Filtered:", input$os_q6, ")"),
      x = "App Usage Time (minutes/day)",
      y = "Number of Apps Installed"
    ) +
    theme_minimal()
})
```


